### 2024-07-07 doc/Thesis/chapter/03-experimental.tex
edit until excl. Pre-optimization of Coating Procedure

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Aqueous Precursor Solutions}
\label{sec:exp-sol-aq}
\gls{zrpro} was added to acetylacetone (\gls{acac}) while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to isopropyl aclohol (\gls{ipo}) and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the homogeneity of the resulting layer. %(in terms of what?)}. % \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the \gls{zrpro}-gls{acac} solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
%Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
Unfortunately, this solution failed to produce homogeneous layers, but instead only resulted in sparse patches of \gls{zro} on the substrate.
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aqueous solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Buthanolic Solution}\label{sec:exp-sol-bu}
%\todo{what did you did you do percisely! It must be logical and should be followed}
Five different concentrations of the buthanolic solutions were prepared.
\ds{
\td{Not all (which?)} chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
}
The base recipe (\gls{1f}) was inspired by Hu~et~al.\cite{Hu2016}.
\Gls{buoh}, \gls{zrpro}, \gls{acac} and \gls{ipo}/\gls{acoh} were used as solvent, precursor, chelating agent and stabilization agent, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tape Casting}
\label{sec:exp-db}
All glass substrates were doctor bladed manually with a smooth stainless steel wire bar coater. 
On two opposing edges adhesive tape was applied to create a valley in between. 
After the layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
%\td{(at which T?)}.
Lower \gls{db} velocities resulted in less homogeneous layers.
Thus, the \gls{db} velocity was not altered in the manual \gls{db} process. 
One and two layers of adhesive tape were used to alter the depth of the valley.

%Most steel substrates (all pre-optimization and optimization samples) 
%All 
Steel substrates were doctor bladed with an Erichsen Coatmaster 510 film applicator with a heatable plate.
%The rest was doctor bladed on a glass plate, initially fixed with double sided adhesive tape and 
%partially heated with a heat gun.
%The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in \SI{0.05}{\milli\meter} steps and \td{did not substantially alter the results. (what do you mean?)}
%For the rest of the experiments a blade height of \SI{0.2}{\milli\meter} was used.
All experiments were performed with a blade height of \SI{0.2}{\milli\meter}.
%
%Eventually, a heatable vacuum plate was used. It 
The heatable vacuum plate had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where underpressure could be applied to keep the substrate in place. 
Most of them were covered with tape (see figure~\ref{fig:eric}) to increase the suction intensity at the remaining ones.
After setting the temperature of the heating plate to \SI{200}{\celsius}, the temperature of the vacuum plate 
(room temperature, \SI{40}{\celsius}, \SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) 
and the \gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
the blade was put into its initial position, the sample was placed on the vacuum plate and the vacuum 
was switched on. 
During pre-optimization, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
\mmps{1}, \mmps{2} and \mmps{5}) were tested. 
\ul{100} of solution were 
applied with a 10 - \ul{1000} pipette and the blade moved over the sample distributing the 
liquid evenly. After evaporation of the solution, the vacuum was turned off, the 'blade 
pusher' was put into initial position, the blade was removed and excess solution 
was removed from the plate with a wipe. 
The coated substrate was dried for \minutes{5} on a \SI{200}{\celsius} heating plate.
%\td{transferred to the \SI{200}{\celsius} heating plate and rested on there for \minutes{5}. (why? what was the purpose?)}
This process of applying a \gls{zro} layer was repeated as many times as needed.
\begin{figure}
	\centering
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsen1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsendb1.png}
		\caption{}
	\end{subfigure}
	\caption{
		(a)
		Temperature regulator (\underline{1}) on the left,
		vacuum pump (\underline{2}) in the background and 
		Erichsen Coatmaster 510 film applicator (\underline{3}) with heatable vacuum plate.
        (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\milli\meter}.
		The majority of the suction areas is sealed with tape to increase the underpressure at the remaining ones.
	}
	\label{fig:eric}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-1.png}
		\caption{}
		\label{fig:micro1}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-2.png}
		\caption{}
		\label{fig:micro2}
	\end{subfigure}
	\begin{subfigure}{\textwidth}
		\centering
		\begin{circuitikz} \draw
			(0,0) to[european voltage source] (0,2)
			to[ammeter] (2,2) 
			to[generic,l=W] (4,2) 
			to[generic,l=Au] (6,2) 
			to[generic,l=Al] (8,2)
			-- (8,2)
			to[generic,l=ZrO$_2$] (8,0)
			-- (8,0)
			to[generic,l=steel] (6,0)
			to[generic,l=Ag] (4,0)
			to[generic,l=Au] (2,0) 
			to[generic,l=W] (0,0) 
				;
		\end{circuitikz}
		\caption{}
		\label{fig:circuit}
	\end{subfigure}
	\caption{View of a sample through the microscope attached to the multimeter and sketch of circuit. 
	\label{fig:micro}
	(a) Sputtered silver contacts on sample with gilded wolfram contact probe touching one of the contacts. 
	(b) Edge of a sample with the probe touching silver paste on top of a sanded patch.
	(c) From the voltage source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe. }%\td{(what is XXX circuit?)}}
\end{figure}

The \gls{iv} curves were measured with Agilent 4156C Precision Semiconductor 
Parameter Analyzer from \SI{-0.5}{\volt} to \SI{0.5}{\volt} with steps of 
\SI{10}{\milli\volt}.
Prior to \gls{iv} measurements the samples were sputtered with aluminium 
through a mask to produce a multitude of equidistant contacts with a Leybold 
UNIVEX450C Sputter System.
Directional current sputtering was used with argon as inert gas at \SI{0.005}{\milli\bar} 
and with a power of \SI{40}{\watt} for \SI{700}{\second}.
Between sputtering and \gls{iv} measurements 
direct contacts to the steel substrate were created by removing a patch of the \gls{zro}
layer with 
sand paper on two opposing edges of a sample and then by applying silver paste.
See figure~\ref{fig:circuit} for a sketch of the connectivity.

@@

The average of each conductance would be an easy and naive choice but difficult to represent a 

@@

to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms and shall be called conducticity hereafter for lack of a better term. 

@@

Another measure is the density of shorted species $\rho$ (pinhole density), calculated in following way:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREOPTIMIZATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pre-optimization of Coating Procedure}
\label{sec:exp-preopt}
%\td{preopt of what? recipe?}
%\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
%\td{Screening}
%244 - 93 aqueous - 103 testing - 191 buthanol - 206 preopt - 244 emma
% 93 aq - 20 adapting Hu2016 - 88 testing process vars - 15 pre-opt - 38 emma (3 failed samples)
244 samples were produced: 93 samples with the aqueous recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimization to find fitting constraints for the final optimization (see section \ref{sec:ss}).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Aqueous Precursor Solutions}
\label{sec:exp-sol-aq}
\gls{zrpro} was added to acetylacetone (\gls{acac}) while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to isopropyl aclohol (\gls{ipo}) and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the homogeneity of the resulting layer. %(in terms of what?)}. % \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the \gls{zrpro}-gls{acac} solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
%Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
Unfortunately, this solution failed to produce homogeneous layers, but instead only resulted in sparse patches of deposits on the substrate.
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aqueous solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Buthanolic Solution}\label{sec:exp-sol-bu}
%\todo{what did you did you do percisely! It must be logical and should be followed}
Five different concentrations of the buthanolic solutions were prepared.
\ds{
\td{Not all (which?)} chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
}
The base recipe (\gls{1f}) was inspired by Hu~et~al.\cite{Hu2016}.
\Gls{buoh}, \gls{zrpro}, \gls{acac} and \gls{ipo}/\gls{acoh} were used as solvent, precursor, chelating agent and stabilization agent, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tape Casting}
\label{sec:exp-db}
All glass substrates were tape-casted manually with a smooth stainless steel wire bar coater. 
On two opposing edges adhesive tape was applied. %to create a valley in between. 
This allowed material to only be deposited on the area between the tape.
After the layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
%\td{(at which T?)}.
Lower \gls{db} velocities resulted in less homogeneous layers.
Thus, the \gls{db} velocity was not altered in the manual \gls{db} process. 
One and two layers of adhesive tape were used to alter the depth of the valley.

%Most steel substrates (all pre-optimization and optimization samples) 
%All 
Steel substrates were doctor bladed with an Erichsen Coatmaster 510 film applicator with a heatable plate.
%The rest was doctor bladed on a glass plate, initially fixed with double sided adhesive tape and 
%partially heated with a heat gun.
%The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in \SI{0.05}{\milli\meter} steps and \td{did not substantially alter the results. (what do you mean?)}
%For the rest of the experiments a blade height of \SI{0.2}{\milli\meter} was used.
All experiments were performed with a blade height of \SI{0.2}{\milli\meter}.
%
%Eventually, a heatable vacuum plate was used. It 
The heatable vacuum plate had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where underpressure could be applied to keep the substrate in place. 
Most of them were covered with tape (see figure~\ref{fig:eric}) to increase the suction intensity at the remaining ones.
After setting the temperature of the heating plate to \SI{200}{\celsius}, the temperature of the vacuum plate 
(room temperature, \SI{40}{\celsius}, \SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) 
and the \gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
the blade was put into its initial position, the sample was placed on the vacuum plate and the vacuum 
was switched on. 
During pre-optimization, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
\mmps{1}, \mmps{2} and \mmps{5}) were tested. 
\ul{100} of solution were 
applied with a 10 - \ul{1000} pipette and the blade moved over the sample distributing the liquid evenly. 
After evaporation of the solution, the vacuum was turned off, the pushing bar
%'blade pusher' \td{film applicator, travel pusher, traverse something, pushing bar} 
was put into initial position, the blade was removed and excess solution was removed from the plate with a wipe. 
The coated substrate was dried for \minutes{5} on a \SI{200}{\celsius} heating plate.
%\td{transferred to the \SI{200}{\celsius} heating plate and rested on there for \minutes{5}. (why? what was the purpose?)}
This process of applying a \gls{zro} layer was repeated as many times as needed.
\begin{figure}
	\centering
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsen1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsendb1.png}
		\caption{}
	\end{subfigure}
	\caption{
		(a)
		Temperature regulator (\underline{1}) on the left,
		vacuum pump (\underline{2}) in the background and 
		Erichsen Coatmaster 510 film applicator (\underline{3}) with heatable vacuum plate.
        (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\milli\meter}.
		The majority of the suction areas is sealed with tape to increase the underpressure at the remaining ones.
	}
	\label{fig:eric}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-1.png}
		\caption{}
		\label{fig:micro1}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-2.png}
		\caption{}
		\label{fig:micro2}
	\end{subfigure}
	\begin{subfigure}{\textwidth}
		\centering
		\begin{circuitikz} \draw
			(0,0) to[european voltage source] (0,2)
			to[ammeter] (2,2) 
			to[generic,l=W] (4,2) 
			to[generic,l=Au] (6,2) 
			to[generic,l=Al] (8,2)
			-- (8,2)
			to[generic,l=ZrO$_2$] (8,0)
			-- (8,0)
			to[generic,l=steel] (6,0)
			to[generic,l=Ag] (4,0)
			to[generic,l=Au] (2,0) 
			to[generic,l=W] (0,0) 
				;
		\end{circuitikz}
		\caption{}
		\label{fig:circuit}
	\end{subfigure}
	\caption{View of a sample through the microscope attached to the multimeter and sketch of circuit. 
	\label{fig:micro}
	(a) Sputtered silver contacts on sample with gilded wolfram contact probe touching one of the contacts. 
	(b) Edge of a sample with the probe touching silver paste on top of a sanded patch.
	(c) From the voltage source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe. }%\td{(what is XXX circuit?)}}
\end{figure}

The \gls{iv} curves were measured with Agilent 4156C Precision Semiconductor Parameter Analyzer from \SI{-0.5}{\volt} to \SI{0.5}{\volt} with steps of \SI{10}{\milli\volt}.

Top contacts for the I-V measurements were formed 
with a Leybold UNIVEX450C Sputter System.
by sputtering 200 nm of aluminum through a shadow mask, defining circular contacts of a diameter approximately \SI{6}{\milli\meter}. 
The bottom contacts to the steel substrate or to the ITO- or FTO-coated glass were formed by removing the ZrO2 deposit from a corner of the substrate, by soft abrasion with sand paper, and then applying conductive silver paste.     
%Prior to \gls{iv} measurements the samples were sputtered with aluminium through a mask to produce a multitude of equidistant contacts with a Leybold UNIVEX450C Sputter System.
%Directional current sputtering was used with argon as inert gas at \SI{0.005}{\milli\bar} and with a power of \SI{40}{\watt} for \SI{700}{\second}.
%Between sputtering and \gls{iv} measurements direct contacts to the steel substrate were created by removing a patch of the \gls{zro} layer with sand paper on two opposing edges of a sample and then by applying silver paste.
See figure~\ref{fig:circuit} for a sketch of the connectivity.

The measured I-V curves therefore represent the vertical resistance of the deposited layer. 
This resistance will be predominantly influence by the presence of shunts (hotspots or short-cuts between the top and bottom contact), appearing due to the inhomogenous thickness, and pinholes through the ZrO2 layer.

@@

The average of each conductance would be an easy choice but difficult to represent a 

@@

to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms and shall be called conductivity hereafter. % for lack of a better term. 

@@

Another measure is the density of shorted elements $\rho$ (pinhole density), calculated in following way:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREOPTIMIZATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pre-optimization of Coating Procedure}
\label{sec:exp-preopt}
%\td{preopt of what? recipe?}
%\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
%\td{Screening}
%244 - 93 aqueous - 103 testing - 191 buthanol - 206 preopt - 244 emma
% 93 aq - 20 adapting Hu2016 - 88 testing process vars - 15 pre-opt - 38 emma (3 failed samples)
% 244 samples were produced: 93 samples with the aqueous recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimization to find fitting constraints for the final optimization (see section \ref{sec:ss}).
